A tutorial on Generalised Additive Mixed Effects Models for bilingualism research

### 2024-10-08 manuscript/manuscript.qmd
add docx version

---
title: "A tutorial on Generalised Additive Mixed Effects Models for bilingualism research"
format:
  pdf:
    keep-tex: true
    number-sections: true
editor: visual
bibliography: gam_refs.bib
csl: apa.csl
---

>>>>

---
title: "A tutorial on Generalised Additive Mixed Effects Models for bilingualism research"
format:
  docx:
    number-sections: true
  pdf:
    keep-tex: true
    number-sections: true
editor: visual
bibliography: gam_refs.bib
csl: apa.csl
---
